Team FSU at ReNeuIR 2024

### 2024-06-24 paper/paper-pre.tex
mf

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX{} document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as well as many
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  LaTeX class \sep
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% General Statement
% - distillation +/- score injection improve cross-encoder
%
% Specific Problem
% - unclear, if the two approaches transfer to tiny/smaller models
% Outline proposed solution
% Transfer two approaches to TinyBERT
%
% Evaluation: clear
%
  We describe the submission of team FSU in the ReNeuIR~2024 shared task on reaching efficiency in neural information retrieval. Previous work has shown that distillation and score injection are two approaches to make cross-encoders more effective. Still, the cross-encoders used in this previous works were rather big and hence not the most ``efficient'' ones. try to transfer two techniques that help to improve the effectiveness of cross-encoders to tiny models. We transfer {\color{red} ...}. Our experiments show {\color{red}...}.
%
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Tiny Cross Encoder \sep
  Efficient Re-Ranking \sep
  Distillation \sep
  BM25 Score Injection
\end{keywords}
